Investigating soundscapes perception through acoustic scenes simulation

### 2018-06-21 v2/responseToReviewers.tex

\documentclass[10pt]{article}

\title{Reply to reviewer concerning submission """}

\begin{document}

\maketitle

\section{Answer to Reviewer 1}

\begin{enumerate}

\item \emph{The utility of this tool beyond the experiments presented here is not apparent because the flexibility of the system was not demonstrated, for example:
- SimScene itself was only used in the first experiment, and other applications of it were not considered. Design choices vary widely between researchers and domains, meaning that the specific instantiations here may not be generally useful.
- It is not clear how this tool would be expanded to consider other acoustic parameters of interest, beyond level. It might be useful to consider potential relationships to other soundscape softwares such as TAPESTREA, and how the exploration of other acoustic parameters could be made intuitive for experiment participants.}

$\rightarrow$

\item \emph{In the last sentence of the abstract, the distinction of 'physical descriptors' vs. 'global descriptors'  does not have enough context here to be informative.}

$\rightarrow$

\item \emph{In section 2.1 (pg. 5), the citations (particularly 27-31) do not seem relevant for justifying the event/texture distinction in the simulator.}

$\rightarrow$

\end{enumerate}

\end{document}

### 2018-06-21 v1/lafaySimulatedScenePerception.tex
response

Among the 44 subjects, 40 succeeded, producing at the end 80 simulated sound scenes (40 ideal scenes, 40 non ideal scenes). the 4 other subjects were excluded from the process due to a lack of understanding of the instructions or failure to respect them, or for exceeding the maximum duration allowed to perform the experiment.

>>>>

Among the 44 subjects, 40 succeeded, producing at the end 80 simulated sound scenes (40 ideal scenes, 40 non ideal scenes). the 4 other subjects were excluded from the process due to a lack of understanding of the instructions or failure to respect them, or for exceeding the maximum duration allowed to perform the experiment.  The software platform used for the experiment, the parametrization of the software platform for each generated scene, as well as a 2 dimensional projection of the resulting scenes are available \url{http://soundthings.org/research/urbanSoundScape/XP2014}. The resulting waveforms are available for download \url{https://archive.org/details/soundSimulatedUrbanScene}.
